Modelling the Retinotectal projection - can competition provide a stopping mechanism?

### 2020-03-10 paper/notes.tex
A few more notes

The initial model is very similar to that in the Barrels paper. However,
instead of providing interacton parameters ($\gamma_{i,j}$) in a configuration
file, I allow the config to specify $N$ neurons originating in the retina; I
automatically arrange these in a radially symmetric pattern, and then
automatically obtain the $gamma$ parameters from the neuron locations within
the pattern.

>>>>

The initial model is very similar to that in the Barrels paper. However,
instead of providing interaction parameters ($\gamma_{i,j}$) in a configuration
file, I allow the config to specify $N$ neurons originating in the retina; I
automatically arrange these in a radially symmetric pattern, and then
automatically obtain the $gamma$ parameters from the neuron locations within
the pattern.

\subsection{Configurations}

In the config directory, there are numerous basic configs, such as N12.json,
N24.json and so on. I find I have to modify some of the parameters as N
increases. Larger N requires smaller hexes to allow a suitable pattern to
develop. Larger N also generally requires a smaller diffusion constant
$D$. I'm experimenting with $\epsilon$, the competition parameter, which, if
too high causes the retinotopy to degrade during the simulation.
